Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex

\subsection{Continual Learning}
% Definition of CL -> a sequence of tasks

@@

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
	\input{tables/img_super.tex}
\end{table}
\subsection{Updating the representation during continual learning}

>>>>

\subsection{Sparse functional regularization (SFR) in Continual learning}
% Definition of CL -> a sequence of tasks 
In this paper we consider the Continual learning setting were a sequence of disjoint sets

@@

    % THE TABLE NUMBER ARE GENERATED BY A SCRIPT	
	\input{tables/img_super.tex}
\end{table}

Similarly to the UCI experiments, we trained neural networks (CNN, architexture matches \citet{immerImprovingPredictionsBayesian2021}) for the FMNIST and CIFAR10 classification tasks. After training, we computed the duals for NN2SVGP and used the resulting SVGP for uncertainty estimates, see \cref{tbl:imagesuper}. We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert]. We ran the experiment over $5$ seeds. During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.

In addition to uncertainty estimates, our method can update the posterior when given new data. We gave the SVGP model 10 \% of the test dataset used for evaluation, and compare the performance of the SVGP model and the retrained NN in [INSERT TABLE].

\subsection{Updating the  network representation for Continual learning}
The Continual learning setting is a challenging and the training and
